Predicting Sales Level for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2016-12-09 paper.tex
Added main steps of the methodology
@amorag please check :)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%First you have to explain why it is enough to predict the level of
%sales, and not the precise number. 
An important task when publishing a new book is determining an accurate number 
of copies to be printed. Doing both an under- or an overestimation will lead to financial losses.
In this paper, we address the problem of predicting total sales using cost-sensitive ensemble methods.
% Antonio - explain briefly what are them
These can be used as reliable decision-aid tools for publishers, as a part of the final stages of the editorial process. 
Thus, a real dataset including the complete sales data for books published in Spain across several years has been used to compute the prediction models.
% Antonio - extend a bit this with the followed methodology.
% Explain also the method you are using and why it's an improvement
% over the previous one - JJ
We evaluate our approach on the real data collected by a Spanish publishing company.
Results show that %\emph{EXPLAIN THE RESULTS OBTAINED}.

@@

Reliable sales prediction can enhance the whole production process for different companies involved in manufacturing, marketing and trading.

Specifically, focusing in the publishing process of a new book, deciding the optimal {\em
  print run}, i.e. the number of copies to be printed and delivered to
bookstores, is a very challenging problem, that is why it is extremely
important to develop accurate predictive models which could forecast
the future sales a new book will achieve, in order to optimise
production schedules: to improve the publishing company profits and to
minimise losses \cite{Zhao2001}, due both to the excess or to the
scarcity of units. 
%I would eliminate this paragraph. We have it on the other one.
Since, according to the results reported in \cite{Fildes2010,Saeed2008}, reducing the error in estimated sales leads to an enhancement of the whole production process.

Usually the prediction of book sales has been generally based on experts' experience. They analyse data about sales and, taking into account their knowledge of the industry, the production process, and their perception about trends, and take decisions on the production and publication process.
However, this process might be tedious, especially when the amount of data is 
quite large. Moreover, the results are not robust, since different experts can reach different predictions from the same dataset \cite{Sanders1994}.

%\textbf{UNDER CONSTRUCTION}
% Antonio - I remove the ';)' because I want to check the parentheses
% correspondence and it breaks it. :P
% Use comments for non-text comments. Like under construction - JJ
% Define level of sales before you use it here. Is it the actual
% number? A ballpark? If it's the actual number, it should be unit
% sales - JJ 
To make the print run as close as possible to the actual level of sales, it is 
essential to have an estimation of those sales. 
In this sense, this paper continues our previous work on book sales prediction 
\cite{Castillo2016books} in which the main factors influencing sales where 
analyzed in order to create a tool that the publisher can use to decide how many 
books should be printed.
In that paper, several regression methods were applied to estimate sales for new launched books using a real dataset of book sales related to the Spanish market, provided by the Spanish publishing company Trevenque Editorial S.L.\footnote{\tt http://editorial.trevenque.es}

However, since finding adequate forecasting techniques and selecting the best method 
to use represents also a problem, we propose configuring complex models based on
ensembles \cite{Qiu2014} in order to determine the actual 
level of sales a new book will achieve.
Moreover, since publishers need models to explain obtained predictions, and 
`black box' forecasting methods may not be suitable, using these ensemble 
models publishers will be able to combine their expert knowledge about the 
market with the created forecasting models in order to get a reliable estimation 
of book sales level.

% Antonio - We must remark that this approach is based in classification rather than regression, which is based on levels of sales (classes) instead of on numerical results. These will be easily 'explained' or justified for a (human) publisher.
% Previous work also presented the results in an intelligible way, since it offered decision trees as the last output, but they include regression computation in the leaves. Here the models/outputs will be easily interpreted.

The rest of this paper is structured as follows: 
A detailed review of the approaches related to sales prediction in similar scopes is presented in Section \ref{sec:soa}.
Then, Section \ref{sec:methodology} details the methodology considered in the present study. 
Obtained results after extensive experimentation are presented in Section \ref{sec:experiments_results}.
Finally, conclusions and future lines of work are presented in Section \ref{sec:conclusions_future_work}.

@@

Sales prediction is an important problem that can improve the quality of business 
strategy for different companies. 
Traditionally, sales prediction problems have been solved using advaced methods 
such as regression models \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999}, 
fuzzy systems \cite{Mastorocostas2001}, or mixture of methods \cite{Chang2006715,Meulstee2008,ChiJie2012}.

The most used technique to tackle sales forecasting problems is time-series prediction methods
\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990,KayacanUK10},
however the correctness of the problem data strongly affects the predictions obtained.
Moreover, this kind of methods are based on using historical data to make time series.
However, in the case of new products sales prediction (such as the issue of new books), 
there is no available historical sales data \cite{ChingChin2010}, 
and only pre-sales data are available \cite{FaderHardie2005,Madsen2008}, 
i.e. variables known before the product is on sale.

Not only the lack of historical data makes this a complex problem, but also the fact 
that several variables (seasonality, promotions, or fashions) might influence predictions
\cite{Lapide1999,Thomassey2012,Xia2012,SThomassey2014,ChernWSF15}.

Due to the difficulty this problem represents when forecasting sales of new 
products, some authors have proposed using different data mining methods, such as
data clustering and fuzzy neural networks \cite{Chang2009}  or
extreme learning machine with adaptive metrics of inputs \cite{Xia2012}.
In this sense, several authors have proposed using ensemble of models for sales forecasting, 
as in \cite{ChiJie2012}, where a hybrid forecasting model integrates ensemble 
empirical model decomposition and extreme learning machine to develop an effective 
forecasting model for computer products sales.
Also, Meulstee et al. \cite{Meulstee2008} developed an ensemble learning approach 
for better handling of seasonal changes and fluctuations in consumer demands,
while Chang et al. \cite{Chang2006715} integrated a fuzzy logic controller 
and artificial neural network for sales forecasting in printed circuit board industry.
Another authors have faced the problem of sales forecasting in textile-apparel 
fashion industry (a very similar issue to the new book publishing problem) 
using a clustering method together with decision trees, as in \cite{SThomassey2014},  or
a forecasting method based on extreme machine learning with adaptive metrics of inputs \cite{Xia2012}.

% TODO

@@

@@

In the next stage of the experiments, the ensemble classifiers (i.e. RF, Bagging and AdaBoost) are applied and evaluated. For Bagging and AdaBoost, the base classifier is selected to be the J48 decision tree algorithm. This selection is for three reasons: first, the J48 algorithm achieved very competitive evaluation results in the previous phase. Second, J48 is much faster as a learning algorithm compared to the MLP network which was the second candidate. Third, tree induction algorithms are good candidates as base classifiers in bagging and boosting because support diversity among the learners. It is well known that tree induction algorithms are relatively unstable (i.e. weak) base learners, meaning that small changes in the training data lead to big changes in the developed models.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%First you have to explain why it is enough to predict the level of
%sales, and not the precise number. 
% Antonio - it is true, but how can we justify this, JJ?
% I guess that precision is relative in this kind of methods, since the publisher is not going to print exactly '237' books due to it is the output of a regression method. Instead, there could be a range of books to be printed (as a standard) related with an expected 'low', 'medium', 'high' or 'very high' amount of sales.
% Moreover, I guess that the classification output, considering four classes would work better (more precisely and close to reality) than regression.
% What do you think?
An important task when publishing a new book is determining the number 
of copies to be printed, since doing both a (dramatic) under- or overestimation will lead to important financial losses.
In this paper, we transform this problem into a classification one, defining different sales levels i.e. classes. 
The obtained results will be easier to interpret by publishers than other black-box techniques, 
so these methods can be used as reliable decision-aid tools for publishers, to be considered in their decision as a part of the final stages of the editorial process.

The problem of predicting these levels has been addressed applying cost-sensitive ensemble methods.
% Antonio - explain briefly what are them  and  the followed methodology.
In order to do so, a real dataset collected by a Spanish publishing company, including the complete sales data for books published in Spain across several years, has been used to design and evaluate the prediction models.
% Explain also the method you are using and why it's an improvement over the previous one - JJ
Results show that %\emph{EXPLAIN THE RESULTS OBTAINED}.

@@

Reliable sales prediction can enhance the whole production process for different 
companies involved in manufacturing, marketing and trading.
Moreover, in some real-world cases, such as consumer electronics, fashion products and books, new products are presented/launched every season; thus, accurate sales forecasting models could help in marketing campaigns for instance.

Specifically, focusing in the publishing process of a new book, deciding the optimal {\em  print run}, i.e. the number of copies to be printed and delivered to bookstores, is a very challenging problem. Thus, it is extremely
important to develop accurate predictive models which could forecast
the future sales a new book will achieve, in order to optimise
production schedules \cite{Fildes2010,Saeed2008,Zhao2001}, to improve the publishing company profits and to minimise losses, due both to the excess or to the scarcity of units. 
%I would eliminate this paragraph. We have it on the other one.
%Since, according to the results reported in \cite{Fildes2010,Saeed2008}, reducing the error in estimated sales leads to an enhancement of the whole production process.
% Antonio - I agree. Removed

Traditionally the prediction of book sales has been generally based on experts' experience. They analyse data about sales and, taking into account their knowledge of the industry, the production issues, and their perception about trends, take decisions on the production and publication processes.
However, this procedure might be tedious, especially when the amount of data is 
quite large. Moreover, the results are not robust, since different experts could come to different predictions from the same dataset \cite{Sanders1994}.

% TODO: UNDER CONSTRUCTION
% Define level of sales before you use it here. Is it the actual
% number? A ballpark? If it's the actual number, it should be unit
% sales - JJ 
% Antonio - done in a paragraph below
It is also possible to use any kind of decision-aid tool, such as estimating or predictive models. These should be able to compute an accurate number of expected sales which can help the publisher (expert) to take the optimal decision. 
Thus, in our previous work \cite{Castillo2016books}, the main factors influencing sales where analyzed in order to create that kind of tool.
In that paper, several regression methods were applied to estimate sales for new launched books using a real dataset of book sales related to the Spanish market, provided by the Spanish publishing company Trevenque Editorial S.L.\footnote{\tt http://editorial.trevenque.es}.

% Antonio - this is themotivation/justification of the present work. Please all chek it. ;D
However, the complexity of those models, even if they yielded a decision tree might be a flaw for publishers when they must work with them in real scenarios, since the leaves of those trees are complicated regression formulae.
In addition, the estimated number despite being accurate according to the experiments, might not be very reliable for these experts, in the sense that most of them would prefer to deal with categorical variables to include in their own `prediction formulae'.

Thus, having in mind `the human factor' of the print-run decision process, in this paper we have addressed the problem from a new perspective. We have defined, with the help of an expert, different \textit{levels or ranges of sales}, composing different incremental categories: \textit{Low, Medium, High} and \textit{Very High}. Then, these have been considered as classes, so the given dataset has been labelled according to them, and the problem has been faced as a classification one.

Moreover, handling the problem as a classification task let us to emphasize on the ranges which could be more `critical', e.g. the most profitable books (High and Very High categories). Thus, we can penalize more the misclassification of these categories and, consequently, this tool will perform a better identification of successful books than our previous approach \cite{Castillo2016books}.
% which will be definitely very interesting for publishers.

In order to solve this problem, in this work we propose configuring complex models based on ensembles \cite{Qiu2014} in order to determine the actual level of sales a new book will achieve.
% Antonio - justify why ensembles have been chosen instead of other classification approaches: accuracy, perform, easier to interpret, faster, ...
Another advantage of the proposed approach is that they are easier to interpret than `black box' forecasting methods, such as regression techniques. So, using these ensemble methods, publishers will be able to combine their expert knowledge about the 
market with the obtained models in order to get a reliable estimation 
on book sales level. Moreover, as the output will be just a class, they will be able to understand and justify better their decision.

% Antonio: TODO - explain how are we going to demonstrate the value of this proposal and how are we going to prove that it is better than our previous approach... Will it 'better' or just 'different' and also valid as a decision tool? Will we count with an expert to compare them? Maybe JJ could be the Expert? :D

% Antonio: TODO - rewrite with the final structure
The rest of this paper is structured as follows: 
A detailed review of the approaches related to sales prediction in similar scopes is presented in Section \ref{sec:soa}.
Then, Section \ref{sec:methodology} details the methodology considered in the present study. 
Obtained results after extensive experimentation are presented in Section \ref{sec:experiments_results}.
Finally, conclusions and future lines of work are presented in Section \ref{sec:conclusions_future_work}.

@@

%Sales prediction is an important problem that can improve the quality of business strategy for different companies. 
% Antonio - not needed to mention this again in this section. Maybe we can move it to the introduction. ;)
Traditionally, sales prediction problems have been solved using advanced mathematical and machine learning-based methods
% Antonio - why are they 'advanced'?
such as regression models \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999}, fuzzy systems \cite{Mastorocostas2001}, or mixture of methods \cite{Chang2006715,Meulstee2008,ChiJie2012}.

In this line, the most used techniques to tackle sales forecasting problems have been time-series prediction
\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}. %,KayacanUK10}. % Antonio - the last reference doesn't exist
However these methods are strongly dependent on problem data, so the obtained predictions are highly affected by their correctness.
Moreover, this kind of methods are based on using historical data to make time series. However, in the case of new products sales prediction (such as the issue of new books), there is no available historical sales data \cite{ChingChin2010}, 
and only pre-sales data are available \cite{FaderHardie2005,Madsen2008}, 
i.e. variables known before the product is on sale. 
% Antonio - We should rewrite this, since a similar sentence was a weak asseveration in previous paper. The proposed methodology also uses historical data to infer the print-run of new books, so, why is this a problem for Time Series and it is useful for the proposed methods? :/

Not only the lack of historical data makes this a complex problem, but also the fact that several `external' variables (seasonality, promotions, or fashions) might influence predictions
\cite{Lapide1999,Thomassey2012,Xia2012,SThomassey2014,ChernWSF15}.
% Antonio - choose just a couple of references to justify this. ;)

Due to the difficulty this problem represents when forecasting sales of new 
products, some authors have proposed using different data mining methods, such as data clustering and fuzzy neural networks \cite{Chang2009} or extreme learning machine with adaptive metrics of inputs \cite{Xia2012}.
In this line, several authors have applied the ensemble of models for sales forecasting, 
% Antonio - briefly clarify what is an ensemble
as it is done in \cite{ChiJie2012}, where a hybrid forecasting method integrates ensemble empirical model decomposition and extreme learning machine 
% Antonio - learning machine or machine learning?
% Anyway, what does it mean?
to develop an effective forecasting model for computer products sales.
Also, Meulstee et al. \cite{Meulstee2008} developed an ensemble learning approach for better handling of seasonal changes and fluctuations in consumer demands, whereas Chang et al. \cite{Chang2006715} integrated a fuzzy logic controller and an artificial neural network for sales forecasting in printed circuit board industry.

Another authors have faced the problem of sales forecasting in textile-apparel 
fashion industry (a very similar issue to the new book publishing problem) 
using a clustering method together with decision trees, as in \cite{SThomassey2014},  or a forecasting method based on extreme machine learning with adaptive metrics of inputs \cite{Xia2012}.
% Antonio - comment this last paper

Ching et al. \cite{ChingChin2010} used a decision-support system to classify new 
products (tea, cosmetics and soft drink) based on their sales patterns, assuming 
that products in the same class would follow a similar sales pattern. 
In any case, the proposed system can not deal with qualitative data related to the products. 
In this paper, several classification-based approaches have been implemented and tested, also considering categorical data.

%Finally, in those problems where historical data are available, authors have 
%proposed to apply classical time series forecasting methods.
% Antonio - we said previously more or less that Time Series Prediction is not recommended

In \cite{Chang2009} a hybrid model integrating K-Means and fuzzy neural networks 
to forecast the future sales of a printed circuit board is proposed.
% Antonio - compare it with our work
Recent works propose to take advantage of the information extracted from online reviews, such as in \cite{ChernWSF15} where it is conducted an analysis on historical data throughout online reviews, reviewer characteristics, and review influences; in order to understand how electronic `word-of-mouth' influences product sales.
Similar researches took advantage of the information published on specialized 
blogs \cite{Moon2010ICSSSM,Moon2010ICEC}, confirming there is a relationship between the number of blog references and the book sales. Therefore, different sales patterns have been observed by analysing books in series, i.e. the first book published takes the longest period to achieve every single sales scale, while the second book takes the second longest period, and so on.
In these cases, sales forecasting problems can be carried out thanks to a big 
amount of online reviews and historical data.
% Antonio - compare these works and findings with our current work

This paper continues our previous work on the prediction of sales of a new product for which no historical data are available, and where the classical forecasting methods based on time-series are not adequate \cite{Castillo2016books}. In that paper the main factors influencing sales where 
analyzed in order to create a tool, based on several regression methods, that the publisher can use to decide how many books should be printed.

However, in this paper we address the problem of new book sales prediction using cost-sensitive ensemble methods, defining with the help of an expert different \textit{levels or ranges of sales} in order to compose different incremental categories or classes.

@@

\begin{itemize}
\item Data preparation:

\item Select best base classifier:

\item Select best ensemble classifier:

\item Perform cost-sensitive analysis with best ensemble classifiers:

\item Evaluation and comparison:

@@

In the next stage of the experiments, the ensemble classifiers (i.e. RF, Bagging and AdaBoost) are applied and evaluated. For Bagging and AdaBoost, the base classifier is selected to be the J48 decision tree algorithm. This selection is for three reasons: first, the J48 algorithm achieved very competitive evaluation results in the previous phase. Second, J48 is much faster as a learning algorithm compared to the MLP network which was the second candidate. Third, tree induction algorithms are good candidates as base classifiers in bagging and boosting because support diversity among the learners. It is well known that tree induction algorithms are relatively unstable (i.e. weak) base learners, meaning that small changes in the training data lead to big changes in the developed models. Besides the selection of the base classifier, the effect of the number of iterations is experimented in RF, Bagging and AdaBoost as shown in Figures \ref{fig:PerformanceRF}, \ref{fig:PerformanceBagging} and \ref{fig:PerformanceAdaboost}, respectively. Highest prediction rates are obtained at 60 iterations. The best obtained results for these ensemble classifiers are shown in Table \ref{table:ensemble_classifiers}. It can be seen that all ensemble classifiers achieved higher accuracy rates compared to J48 from the previous stage, achieving around 74\% with approximately 4\% improvement. Inspecting the obtained results for VH class, we can notice that although the recall of the VH hasn't improved much compared to J48, the precision has remarkably increased from 74\% to 81.6\%, 80.8\% and 79.3\% for RF, Adaboost and Bagging, respectively. For the H class, there was an improvement for both measurements, recall and precision. RF and Adaboost achieved approximately 68\% and 67\% for recall and precision, while Bagging achieved 67\% and 66\%, respectively. Also, it can be noticed that there is an improvement in general for the other classes, M and L.
